%
% Modified version of the sample_ndthesis.tex
% by Sameer Vijay
% Last Change: Wed Jul 27 2005 14:00 CEST
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Sample Notre Dame Thesis/Dissertation
% Using Donald Peterson's ndthesis classfile
%
% Written by Jeff Squyres and Don Peterson
%
% Provided by the Information Technology Committee of
%   the Graduate Student Union
%   http://www.gsu.nd.edu/
%
% Nothing in this document is serious except the format.  :-)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is *not* a substitute for Donald's orginial documentation.  See
% /afs/nd.edu/usr/local/src/tex/texmf/doc/latex/ndthesis/ndthesis.dvi
% for documentation on the particular commands and whatnot.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% You should *also* have a ND formatting guide to ensure that you have
% all the relevant parts, put the captions in the right place, etc.
% Just because you have this wonderful style classfile doesn't mean
% that it removes *all* the formatting onus from you.  :-)
%
% Normally, you should break all of this stuff up into separate files
% (at the very least, one chapter per file) and use the \input
% command.  This is all one file for brevity's (and clarity's) sake.
%
% Note that you should also have a good Makefile; one that invokes
% LaTeX as many times as necessary (up to 4) and bibtex if necessary.
% One should be included in this distribution.  You may want to modify
% the Makefile to make separate chapters, if necessary.
%
% If you have any suggestions, comments, questions, please send e-mail
% to: ndthesis@gsu.nd.edu
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[textrefs,review]{nddiss2e}

% % uncomment the following line 
% if using chapter-wise bibliography
% \usepackage{chapterbib}
% \renewcommand{\bibname}{Cited Works}
% \renewcommand{\bibsection}{\section{\bibname}}

\begin{document}

\frontmatter

\title{Potential of Opportunistic Relaying\\ {\small\scshape Performance study across wireless interfaces on smartphones} }
\author{Shu Liu}
\work{Dissertation}
\degprior{B.S., M.S.}
\degaward{Doctor of Philosophy\\in\\Computer Science and Engineering}
\advisor{Aaron Striegel}
% \secondadvisor{Gordon Gray}
\department{Computer Science and Engineering}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Front stuff
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\copyrightholder{Shu Liu}
\copyrightyear{2014}
\makecopyright

\begin{abstract}
\end{abstract}

\renewcommand{\dedicationname}{}

\begin{dedication}
  To my husband, Wei, who inspires me to exceed my potential. 
\end{dedication}

\tableofcontents
\listoffigures
\listoftables

\begin{preface}
\end{preface}

\begin{acknowledge}
I would like to thank my advisor, Dr. Aaron Striegel, who helped provide
direction and guidance for this work. Without his trust and support, I would not have had the opportunity to work in such great research projects. I would also like to thank the members of my committee, Dr. Christian Poellabauer, Dr. David Hachen and Dr. Gregory Madey, for their time and support in this process.

I also need to thank all my colleagues who create such a good atmosphere in the group;
Dr. Andrew Blaich, Dr. Yingxin Jiang, Dirk Van Bruggen, Lei Meng, Xueheng Hu, Benjamin Bockdtege, and Rachael Purta.  Also Margaret and Michael, deserve a special thanks because their great supports in the Netsense project. I need to further thank all my friends, Nikhil, Hongsheng and Mehrdad, who always took the time to listen. 
\end{acknowledge}

\begin{symbols} 
\end{symbols}

\mainmatter

%
% Chapter 0 (features)
%
\setcounter{chapter}{-1}
\chapter{FEATURES OF FORMATTING IN THIS EXAMPLE FILE}

This \verb+chapter+ has been added to the original sample file to highlight the
various features with the formatting that conforms to the Graduate school
guidelines --- whether obtained due to the use of \nddiss\/ class file or just
plain good practice.
\begin{itemize}
\item An important thing you might notice is that the title of this chapter 
is not in all CAPS. This is a feature since using \verb+\MakeTextUpperCase{}+ 
is not helpful
when you have a math formula or something that just doesnt go CAPS (for eg.
elemental symbols).
\item If you're looking at a pdf document, the pdf bookmarks (left column) link
to all major textual sections including abstract, toc, lof, lot and
bibliography.
\item In the {\em dedication}, the title name has been modified. So, you know
how to and that it can be done.
\item The entries in the {\em List of figures} and {\em List of Tables} are
single-spaced themselves but are double-spaced from the other.
\item The table captions are not in all CAPS as well for the reason mentioned
above.
\item Appropriate space is left between the \verb+Table xx+ and its
corresponding caption (which is double-spaced itself) as in table \ref{tbl:bogus1}.
\item Tables look much better without the vertical lines (good practice).
\item There is double-spacing between the table entries but single-spacing
within the entry.
\item The chapter (see Chapter \ref{chap:golfing}) or section titles are
double-spaced as mentioned in the guidelines.
\item There is a \verb+subsubsection+ present (eg. section \ref{sec:data}) and
is properly formatted in the TOC.
\item Table \ref{tbl:defs} is an example of the use of \textsf{landscape}
environment in which a normal table is formatted in a {\em landscape} mode.
\item The \textsf{longtable} environment is used in Tables \ref{tbl:votes} and
\ref{tbl:rotated-rankings}, in normal and \verb+landscape+ mode, respectively. The
table captions are formatted properly in both cases.
\item In the table \ref{tbl:votes}, the \verb+footnote+ in the table header 
does not appear at all. This is not an error of the \nddiss\/ class but of the
\textsf{longtable} package.
\item An example of citing a website is shown in the bibliography (see
\citep{gairley2000}) which is formatted using the 
\verb+nddiss2e.bst+
citation style file.
\item A bit of information on the \nddiss\/ class file and the typesetting program
used is included in a box on the last page of the thesis.
\end{itemize}

%
% Chapter 1
%

\include{chapter1}


%
% Chapter 2
%

\include{chapter2}


%
% Appendix
%

\appendix

\include{appendix}


%
% Back stuff
%

% % comment out the following three lines
% if using chapter-wise bibliography

 \backmatter
 \bibliographystyle{nddiss2e}
 \bibliography{dissertation}

\end{document}

% End of ``example.tex''
